05_DESeq_manipulation

### 2019-05-20 analysis/05_DESeq2_manipulate.Rmd
better printout

plot_grid(a,b,c,d,e,f, nrow = 2) 
```

```{r totalDEGs2}
plot_grid(a + theme_minimal(base_size = 8) + theme(legend.position = "none", axis.text.x = element_text(angle = 90)),
          b + theme_minimal(base_size = 8) + theme(legend.position = "none", axis.text.x = element_text(angle = 90)),
          c + theme_minimal(base_size = 8) + theme(axis.text.x = element_text(angle = 90)),
          d + theme_minimal(base_size = 8) + theme(legend.position = "none",axis.text.x = element_text(angle = 90)),
          e + theme_minimal(base_size = 8) + theme(legend.position = "none",axis.text.x = element_text(angle = 90)),
          f + theme_minimal(base_size = 8) + theme(axis.text.x = element_text(angle = 90)),
          nrow = 2, rel_widths = c(0.3, 0.3, 0.4)) 
```

>>>>

plot_grid(a + theme(legend.position = "none"),
          b + theme(legend.position = "none"),
          c,
          d + theme(legend.position = "none"),
          e + theme(legend.position = "none"),
          f,
          nrow = 2, rel_widths = c(0.3, 0.3, 0.4)) 
```
